Enabling GPU Virtualization in Cloud Environments

### 2015-10-23 paper.tex
abstract revisado

\title{Enabling the Use of GPU Virtualization in Cloud Environments}
\author{\authorname{Sergio Iserte, Francisco J. Clemente-Castell\'o, Adri\'an Castell\'o,\\Rafael Mayo and Enrique S. Quintana-Ort\'i}
\affiliation{Department of Computer Science and Engineering\\Universitat Jaume I - Castell\'o de la Plana, Spain}
\email{\{siserte, fclement, adcastel, mayo, quintana\}@uji.es}}

@@

\abstract{The use of accelerators, such as GPUs, to reduce the execution time of GPGPU applications has become more popular during last years. 
These devices increment the computational power of a node thanks to its parallel architecture.
This trend has led several cloud vendors such as Amazon Web Services or some middlewares such as OpenStack to add to their current facilities, or to allow, 
instances of virtual machines equipped with NVIDIA GPUs. 
Accomplishing these needs, the guest hosts must be equipped with GPUs which could be barely utilized if a non GPU-enabled Virtual Machine is running in the host.
The solution presented in this work is based on GPU virtualization and shareability in order to reach an equilibrium between supply and demand of accelerators. 
Hence, we propose to decouple from the nodes, real GPUs by using the virtualization technology called rCUDA. 
With this software configuration, the GPUs can be accessed from any VM getting rid 
of the necessity of having physical GPUs in the guest host. 
Moreover, our project studies the viability of these join by using a public cloud 
service configuration and develops a module for OpenStack middleware in order to 
add the needed support for the virtualized devices and the logic to manage them. 
The results show a feasible configuration which adds flexibility to the current and well-known 
cloud solutions. 
}

>>>>

\title{Enabling GPU Virtualization in Cloud Environments}
\author{\authorname{Sergio Iserte, Francisco J. Clemente-Castell\'o, Adri\'an Castell\'o,\\Rafael Mayo and Enrique S. Quintana-Ort\'i}
\affiliation{Department of Computer Science and Engineering\\Universitat Jaume I - Castell\'o de la Plana, Spain}
\email{\{siserte, fclement, adcastel, mayo, quintana\}@uji.es}}

@@

\abstract{The use of accelerators, such as graphics processing units (GPUs), to reduce the execution time of compute-intensive applications has become more popular during the past few years. 
These devices increment the computational power of a node thanks to its parallel architecture.
This trend has led cloud vendors, as Amazon Web Services, or middlewares such as OpenStack to add to their current facilities   
instances of virtual machines including GPUs. 
To fullfil these needs, the guest hosts must be equipped with GPUs which will be barely utilized if a non GPU-enabled Virtual Machine is running in the host.
The solution presented in this work is based on GPU virtualization and shareability in order to reach an equilibrium between service supply and applications' demand of accelerators. 
Hence, we propose to decouple real GPUs from the nodes by using the virtualization technology rCUDA. 
With this software configuration, GPUs can be accessed from any VM avoiding the need  
of having a physical GPUs in the guest host. 
Moreover, we study the viability of this approach by using a public cloud 
service configuration and develop a module for OpenStack middleware in order to 
add support for the virtualized devices and the logic to manage them. 
The results demonstrate this is a viable configuration which adds flexibility to the current and well-known 
cloud solutions. 
}
